Towards Explainability of Machine Learning Models in Insurance Pricing

### 2019-11-01 manuscript/manuscript.Rmd
naic acronym

Of course, these comments only apply within the actuarial profession. Outside of 
the actuarial profession, communication of results may be more challenging. A 
2017 survey conducted by the Casualty Actuarial and Statistical Task Force of 
the National Association of Insurance Commissioners found that the plurality of
responding regulators identified "Filing complexity and/or a lack of resources 
or expertise" as a key challenge that impedes their ability to review GLMs or 
other predictive models [@naic_summer_2017]. Given that machine learning 
algorithms are generally regarded as more complex than GLMs, this implies that
the challenge of communicating machine learning model results is significant.

>>>>

Of course, these comments only apply within the actuarial profession. Outside of 
the actuarial profession, communication of results may be more challenging. A 
2017 survey conducted by the Casualty Actuarial and Statistical Task Force of 
the National Association of Insurance Commissioners (NAIC) found that the plurality of
responding regulators identified "Filing complexity and/or a lack of resources 
or expertise" as a key challenge that impedes their ability to review GLMs or 
other predictive models [@naic_summer_2017]. Given that machine learning 
algorithms are generally regarded as more complex than GLMs, this implies that
the challenge of communicating machine learning model results is significant.
